### 2015-07-31 Irregular-occ/Irregular-occ.tex
continuado artigo de ocultacoes dos irregulares

As explicited in section \ref{Sec: introducao}

@@

@@

%The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the corrected JPL ephemeris as presented in the section \ref{Sec: Offset}.

>>>>

As explicited in section \ref{Sec: introducao}, there is no consensus on a single model about the region where the irregular satellites were formed. In this work we treat them as having a common origin to the Centaurs and TNOs. In this case, they would be the representative objects of the small TNOs population. Since that small objects at great distances are difficult to study, the irregular satellites can complement this gap.

This idea is supported by the

@@

\textcolor{red}{Falta justificar as funções}

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the corrected JPL ephemeris as presented in the section \ref{Sec: Offset}. The procedure to search for stellar candidates follows the same procedure presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2013}.

For Nereid, the candidates for stellar occultations in 2015 and 2016 was searched using the WFI catalogue in the same way as the predictions for Centaurs and TNOs occultations by \cite{Assafin2010, Assafin2012} and \cite{Camargo2013}. This catalogue contains the stars in the path of Neptune in the sky up to mid-2016. It was generated by observations made at the ESO 2p2 telescope (IAU code 809) using the Wide Field Imager (WFI) CCD mosaic detector. The filter used was the broad-band R filter ESO\#844 with $\lambda_c$ = 651.725 nm and $\Delta\lambda$ = 162.184 nm
